---
name: Freddy Ray Drennan
address: "812 Cameron Drive, Severance, CO 80550"
phone: +1 254 931 8313
email: "drennanfreddy@gmail.com"
twitter: fdrennan
github: fdrennan
linkedin: freddydrennan
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: "000088"
output: vitae::awesomecv
header_includes:
  - \ExecuteBibliographyOptions{useprefix=true}
  - renewcommand{\bibfont}{\normalfont\fontsize{10}{12.4}\sffamily}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(vitae)
source("baretable.R")
```
## Education and Qualifications
```{r degrees, results='asis'}
tribble(
  ~Start, ~End, ~Degree, ~Institution,
  2014, 2017, "BBA Quantitative Finance with Minor in Math",  "The University of Texas at Austin",
  2007, 2008, "Licensed Practical Nurse - Compact State License",   "Army Medical Department Center \\& Schools",
  2006, 2007, "EMT - Combat Medical Technician", "Army Medical Department Center \\& Schools"
) %>% 
  # as.data.frame 
  arrange(-Start) %>% 
  filter(Start > 2000) %>%
  mutate(End = replace_na(End, "")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  mutate(Separator = "") %>% 
  select(Years, Degree, Separator, Institution) %>% 
  baretable()
```
## Employment History
```{r employment, results='asis'}
tribble(
  ~Start, ~End, ~Position, ~Achievement,
  2007, 2008, "\\textbf{Military ICU Nurse}, Darnall Army Medical Center", "\\textit{Treated 1000+ critically ill patients}",
  2008, 2010, "\\textbf{Trauma Nurse}, 555th Forward Surgical Team", "\\textit{War zone trauma nurse in Kunar, Afghanistan}",
  2010, 2016, "\\textbf{Pediatric / ICU Nurse}, Pediatric Services of America", "\\textit{Improved outcomes for pediatric seizure patients}",
  2016, 2017, "\\textbf{Student Mentor}, University of Texas at Austin", "\\textit{Taught R programming}",
  #2017, NA,   "\\textbf{Pediatric Nurse}, Aveanna Healthcare",  "\\textit{Post-NICU home nurse}",
  2017, 2018, "\\textbf{Data Optimization Engineer}, Digital First Media", "\\textit{Maintainer of Quantum R Package}",
  2018,2020,   "\\textbf{Data Scientist}, Digital First Media", "\\textit{Increased profit by \\$2M with linear programming}",
  2019,2020,   "\\textbf{Business Analytics Manager}, Logisticare", "\\textit{Showed predictability in overcharges 90+ days out}",
    2020, NA,  "\\textbf{Senior R Programming Consultant}, BioMarin", "\\textit{Built Centralized Statistical Monitoring Solution}",
  2020, NA,  "\\textbf{Founder}, ndexr.com", "\\textit{A Khan Academy for R Programmers}"

  
) %>%
  arrange(-Start) %>%
  #filter(Start > 2000) %>%
  mutate(End = replace_na(End, "")) %>%
  mutate(Years = paste(Start, "--", End, sep = "")) %>%
  select(Years, Position, Achievement) %>%
  baretable()

# __[Repo Here](https://github.com/fdrennan/ndexr-platform)__
```

## Projects/Responsibilities
* __Centralized Statistical Monitoring__
    * Lead developer for implementing an R/Shiny back-end to test data integrity for research trials
    * Worked with the head bio-statistican to create a plugin system for incorporation of new analyses
    * shinydashboard as package, tested using shinytest, rselenium. Developed with golem (usethis of Shiny)
    * `csm` package fortified with travis, testthat, vignettes. Documented with roxygen2
* __[ndexr.com](http://ndexr.com)__
    * Lead developer and creator of a Reddit analytics platform using AWS, Plumber, and Shiny
    * Converted infrastructure into an e-learning platform, where I teach R in production systems. 
    * Shiny app developed with shinydashboard, golem , elasticsearchr. 
* __Logisticare Auto-Assignment__
    * Formulated mixed-integer program (MIP) to match riders with transportation providers
    * Structured model to run off a containerized, load-balanced, R API
    * Provides improved and up-to-date transportation recommendations 
* __Overrides Classification__
    * A $300K/day problem with high class imbalance and regional variance requiring a multi-model approach
    * Predicted 80%+ of the positive class using clever feature engineering
    * Allowed Logisticare to begin determining problematic transportation providers to renegotiate contracts
* [__Omni-Channel Advertising Optimization__](http://drenr.com/pages/html_files/advertisingOptimization.html)
    * A solo data scientist on a team with four front-end developers
    * Decreased campaign management time from one hour to five minutes per campaign
    * Developed unified and coordinated optimization processes between Adwords, Facebook, and TTD
    * Integrated campaign management linking between Salesforce, Data Warehouse and Quantum platform
* __Adtaxi Mathematics System Administrator__
    * Maintained production servers and administration for the Quantum backend
    * Managed users, software upgrades, deployment, and applications on production servers. 
    * Built an R API framework which prevented the need for RSConnect and resulted in $50K/year savings
* __QuantumR Package__
    * Manages search budget pacing - forces advertising campaigns to spend evenly over a given period
    * Optimizes single-channel Trade Desk / Facebook Campaigns - boosts conversions per dollar
    * Implemented Continuous Integration / Unit Testing 
* [__Distributed Machine Learning by Hand with R and Caret__](https://www.youtube.com/watch?v=Yp1bko0Zd7E)
    * Built EC2 servers to send ML data to AWS and run 40+ models in parallel
    * The entire ML framework was developed by myself
    * Shows familiarity and comfort leading/developing machine learning models 
    
    